Evaluation of the repository

### 2024-08-15 pages/paper_evaluation.qmd
feat(evaluation): add timings

<!-- TODO: Add timings for each from evaluation for reporting
Also issue may be that I can't necessarily disaggregate into reporting and code times-->

>>>>

<!-- Add johnson and kim -->

* @shoaib_simulation_2021 - 1h 56m
* @huang_optimizing_2019 - 1h 28m
* @lim_staff_2020 - 1h 12m
* @kim_modelling_2021
* @anagnostou_facs-charm_2022 - 53m
* @johnson_cost_2021

### 2024-08-15 pages/repo_evaluation.qmd
feat(evaluation): add timings

<!-- TODO: Add timings for each from evaluation for reporting
Also issue may be that I can't necessarily disaggregate into reporting and code times-->

>>>>

<!-- Add johnson and kim -->

* @shoaib_simulation_2021 - 30m
* @huang_optimizing_2019 - 17m
* @lim_staff_2020 - 18m
* @kim_modelling_2021
* @anagnostou_facs-charm_2022 - 19m
* @johnson_cost_2021
